Approximation as Differentiation

### 2025-07-10 main/conclusion.tex
Expand XAI bit.

\paragraph{Integrating XAI techniques with Galois slicing.} \roly{Sketch what this might look like.}
Explainable AI (XAI) techniques like Gradient-weighted Class Activation Mapping (Grad-CAM)~\cite{selvaraju20}
use reverse-mode AD selectively on specific activations, calculating \emph{heat maps} that highlight input
regions contributing to a given classification decision. It might be possible to compose these techniques with
\GPS whilst still preserving useful round-tripping properties; if so this could be a basis for end-to-end
explainability in systems that combine neural networks with traditional symbolic computation.

>>>>

\paragraph{Quantitative Galois slicng and XAI.}  Explainable AI (XAI) techniques like Gradient-weighted Class
Activation Mapping (Grad-CAM)~\cite{selvaraju20} use reverse-mode AD selectively to calculate \emph{heat maps}
(or \emph{saliency maps}) that highlight input regions contributing to a given classification or other
outcome. We would like to investigate quantitative approximation structures where $\top$ represents the
original input image and lower elements represent ``slices'' of the image where individual pixels have been
ablated to some degree (partly removed or blurred). This might allow for composing some of these techniques
with Galois slicing, for use in hybrid systems such as physical simulations with ML-based parameterisations.
